\documentclass[oneside,reqno]{amsbook} 

\input{../header.tex}
\title{Database}
\author{Zijun Yan} 

\begin{document}
\maketitle

\part{Database}

\chapter{Object Relational Mapping}

Transient - an instance that's not in a session, and is not saved to the
database; i.e. it has no database identity. The only relationship such an object
has to the ORM is that its class has a Mapper associated with it. 

Pending - when you Session.add() a transient instance, it becomes pending. It
still wasn't actually flushed to the database yet, but it will be when the next
flush occurs. 

Persistent - An instance which is present in the session and has a record in the
database. You get persistent instances by either flushing so that the pending
instances become persistent, or by querying the database for existing instances
(or moving persistent instances from other sessions into your local session).

Deleted - An instance which has been deleted within a flush, but the transaction
has not yet completed. Objects in this state are essentially in the opposite of
“pending” state; when the session's transaction is committed, the object will
move to the detached state. Alternatively, when the session's transaction is
rolled back, a deleted object moves back to the persistent state.

Changed in version 1.1: The 'deleted' state is a newly added session object
state distinct from the 'persistent' state.

Detached - an instance which corresponds, or previously corresponded, to a
record in the database, but is not currently in any session. The detached object
will contain a database identity marker, however because it is not associated
with a session, it is unknown whether or not this database identity actually
exists in a target database. Detached objects are safe to use normally, except
that they have no ability to load unloaded attributes or attributes that were
previously marked as “expired”.

\chapter{Transaction}

Transaction isolation level

\chapter{Pitfall}

Lacking index on column with delete/update trigger may significantly slow down operations.

\chapter{Hadoop}

\chapter{Spark}

Software as a service (SaaS)

\part{Web}

Node.js

React.js Angular.js Vue.js


\part{Concurrency}
ABA problem
Optimistic vs. Pessimistic locking

\part{Crytography}

blockchain
oracle
smart contract
crytoconcurrency
trust minimised aggrement

sybil resistance mechanisms:
proof of work
proof of stake

51\% attack

gas price

\begin{itemize}
\item Immutable
\item Decentralised
\item Transparent
\end{itemize}

Public key
Private key
Address

\part{Internet}

\chapter{NAPT}

Full cone NAT
Address restricted cone NAT
Port restricted cone NAT
Symmetric NAT

\chapter{STUN RFC3489}



\part{Storage}

RAID

\end{document}
